\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sihao Chen (Benny)} % Your name
\address{sihao@berkeley.edu \\
sihao.dev \\
San Francisco, CA, 94114 \\
(917) 288-2594}

\begin{document}

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill Berkeley, CA
\\ M.Eng. in Electrical Engineering and Computer Science \hfill {\em Aug. 2020-May 2021}
% \\ Coursework: Efficient Algorithms and Intractable Problems, Deep Learning, Advanced Robotics, Computer Security, Principles and Techniques of Data Science, Applications of Parallel Computers

{\bf Northeastern University} \hfill Shenyang, Liaoning, China 
\\ B.Eng. in Software Engineering \hfill {\em Sep. 2016-June 2020}
\\ National Scholarship, First Prize in Contemporary Undergraduate Mathematical Contest in Modeling
% \\ Coursework: Software Engineering, Data Structures and Algorithms, Computer Networks, Introduction to Database, Principles of Computer Organization, Object-Oriented Programming and Design

\end{rSection}

\begin{rSection}{Professional Experience}

{\bf Senior Software Engineer at Zip,} San Francisco, CA \hfill{\em June 2026-Present}
\\ - Building a next-generation agent platform that enables users to create and deploy AI agents for various steps of precurement, including gathering requirements, contracting, and payment.

{\bf Sr. Software Engineer at LinkedIn,} San Francisco, CA \hfill{\em Oct. 2021-Present}
\\ - Built the Sales and Marketing Agents using LangGraph, Claude Agent SDK, Deep Agents. Enabled agents to create ad creatives and manage lead generation forms, reducing manual work for advertisers.
\\ - Led the production rollout of the new billing data pipeline and interface using Java, Rest.li, Samza, Spark, and Airflow, ensuring billing accuracy, timeliness, and resilience to data inconsistency and loss.
\\ - Designed and shipped an AI-powered dynamic spending limit system from end to end, adjusting advertiser limits in real time to unlock early-life revenue, using TensorFlow, XGBoost, and Flyte.
\\ - Modernized a large-scale graph system onto scalable infrastructure, eliminating recurring latency incidents and enabling fast incident response that kept service reliable for advertisers.
% to enable ad content management, billing configurations, customer verification, and permission control, supporting enterprise users in managing millions of ad campaigns, pages, and account users at high transaction frequency.

{\bf Software Engineer at Tesla,} Fremont, CA \hfill{\em June 2021-Oct. 2021}\\Developed the acquisition management platform using Java Spring and C\# ASP.NET. Improved the stability and response time of the used car valuation service.

{\bf Research \& Development Intern at Microsoft,} Beijing, China \hfill{\em Jan. 2020-June 2020}
\\{Designed and implemented a document match plan generation algorithm for the Bing search engine based on deep reinforcement learning, improving the match plan's performance by 57.03\%.}

% {\bf Software Engineering Intern,} Zhuomo Group, Beijing, China \hfill{\em Aug. 2018-Aug. 2018}
% \\{Implemented a RESTful API for smartwatch using Java, Docker, Jenkins, Nginx, and Nexus3.}

\end{rSection}

\begin{rSection}{Projects}
{\bf Love2Go, AI-Powered Travel Agency,} Brex Agent Jam Hackathon\hfill{\em Aug 2025}
\\{Designed and implemented a Hostel-world like travel platform with Gemini and Mistral API. Won \$1k prize sponsored by Omnara (YC S25). See {\href{https://www.linkedin.com/feed/update/urn:li:activity:7366000264480247808/?skipRedirect=true}{LinkedIn post}} for details.}

{\bf Assistive Technology for Navigation, Selection, Pointing, and Clicking in a Mouse-free Environment,} UC Berkeley\hfill{\em Sep. 2020-May 2021}
% \\{Capstone project supervised by Professor Brian A. Barsky at University of California, Berkeley}
\\{Designed and implemented a program that controls computer cursors using real time video input with hand gesture recognition using TensorFlow and C++.}

% {\bf Interactive Prediction using Imitation Learning,} UC Berkeley\hfill{\em May 2019-Sep. 2019}
% % \\{Supervised by Professor Masayoshi Tomizuka at MSC Lab,  University of California, Berkeley}
% \\{Implemented an integrated interactive traffic visualization tool using Uber AVS.}
% \\{Built an imitation learning model for trajectory prediction using PyTorch and OpenCV.}

{\bf Teaming Platform,} UC Berkeley \hfill{\em Sep. 2020-May 2021}
\\{Developed a website that generates customized surveys, accepts survey responses, and generates response analysis using React.js, Firebase, and Cloud Functions, served on Google Cloud Platform.}

% {\bf Joint Project with Uber on Mobility Modeling, } UC Berkeley \hfill{\em Feb. 2019-Mar. 2019}
% % \\{Worked on a joint project with Uber on mobility modeling supervised by Professor Alexandre Bayen.}
% \\{Tested a transportation optimization system, visualized and analyzed data on transportation statistics on a joint project with Uber on mobility modeling }
% {\bf Multimodal Emotion Recognition}\hfill{\em Mar. 2019-May 2019}
% \\ {Supervised by Professor Jungseock Joo, Red Hen Lab, Los Angeles, CA}
% \\{Implemented a deep learning model for human pose estimation using TensorFlow.}
% \\{Designed an integrated system for multimodal emotion recognition. Proposal approved by GSoC 2019.}

% {\bf Human-Machine Synchronization}\hfill{\em Nov. 2017-Jan. 2019}
% \\Supervised by Professor Tao Ren, Northeastern University, Shenyang, Liaoning, China
% \\{Debugged and tested an interactive humanoid robot that imitates human body motion based on Android and Microsoft Kinect. Project earned second prize in Chinese Artificial Intelligence Design Contest.}

\end{rSection}

\begin{rSection}{Skills}
{\bf Programming }Python, Java, Scala, JavaScript (Node.js), MATLAB, C, C++, C\# (.NET), SQL, Go, HTML, CSS, LaTeX, Linux/UNIX Script, AWS, GCP, Git, Gradle %NoSQL, ROS, CUDA, MPI, OpenMP
\\{\bf Language }Fluent in Mandarin Chinese and English. Learning Spanish and French.
\end{rSection}

\begin{rSection}{Publications}
Match Plan Generation in Web Search with Parameterized Action Reinforcement Learning. {\em Proceedings of the Web Conference 2021}. April 2021
\end{rSection}
\end{document}
